---
title: "p8105_hw1_xf2302"
output: github_document
date: "2025-09-19"
---
# Problem 1
# Add initial setup chunk and load required libraries
```{r setup, message=FALSE}
library(moderndive)
library(ggplot2)
```
# Load the dataset
```{r load_data}
data("early_january_weather")
```
# Add dataset summary description using inline R
Within the `early_january_weather` dataset, there are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. Key variables include *temperature* (measured in °F), *humidity* (percentage of air moisture), and *time_hour* (timestamp for each observation). The mean recorded temperature is about `r round(mean(early_january_weather$temp, na.rm = TRUE), 2)` degrees Fahrenheit.

# Add scatterplot of temperature vs time_hour colored by humidity
```{r}
library(tidyverse)
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(
    title = "Temperature vs Time (colored by Humidity)",
    x = "Time (hour)",
    y = "Temperature (°F)",
    color = "Humidity"
  ) +
  theme_minimal()
```

# Export plot
ggsave("scatterplot_temp_time.png", width = 7, height = 5)

# Describe patterns
The scatterplot of temperature (°F) against time_hour, colored by humidity, shows that temperature fluctuates between about 30°F and 55°F, with a mean near 39.6°F. Higher humidity values, indicated by cooler colors, are generally associated with lower temperatures, while lower humidity values align with warmer conditions. A clear cyclical pattern emerges over time, reflecting daily temperature increases during daytime and decreases at night.

# Problem 2
# Create a data frame with different variable types
```{r}
set.seed(123) # for reproducibility

df = tibble(
  norm_sample = rnorm(10),                          # numeric
  above_zero  = rnorm(10) > 0,                      # logical
  char_vec    = letters[1:10],                      # character
  factor_vec  = factor(rep(c("low", "medium", "high"), length.out = 10)) # factor
)

df
```




