---
title: "p8105_hw1_xf2302"
output: github_document
date: "2025-09-19"
---
# Problem 1
# Add initial setup chunk and load required libraries
```{r setup, message=FALSE}
library(moderndive)
library(ggplot2)
```
# Load the dataset
```{r load_data}
data("early_january_weather")
```
# Add dataset summary description using inline R
Within the `early_january_weather` dataset, there are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. Key variables include *temperature* (measured in °F), *humidity* (percentage of air moisture), and *time_hour* (timestamp for each observation). The mean recorded temperature is about `r round(mean(early_january_weather$temp, na.rm = TRUE), 2)` degrees Fahrenheit.

# Add scatterplot of temperature vs time_hour colored by humidity
```{r}
library(tidyverse)
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(
    title = "Temperature vs Time (colored by Humidity)",
    x = "Time (hour)",
    y = "Temperature (°F)",
    color = "Humidity"
  ) +
  theme_minimal()
```






